
\vspace{\vertspace}

{
\renewcommand{\labelitemi}{}
\begin{itemize}


  \item \textbf{Huziy O.}, Sushama L., Diro G. T., Duguay C., Baijnath J., Yerubandi R., 2017.
  Heavy lake effect snow in current and future climate for the Great Lakes region. CNRCWP science meeting, Montreal

  \item \textbf{Huziy O.}, Sushama L., Diro G. T., Duguay C., Baijnath J., 2017.
  On the representation of heavy lake-effect snow events for the Laurentian Great
  Lakes region in a Regional Climate Model. EGU, Vienna, Austria.


  \item \textbf{Huziy O.}, Sushama L., 2016. Lake-river and lake-atmosphere
  interactions in a changing climate over Northeast Canada. CMOS, Fredericton, Canada.

  \item \textbf{Huziy O.}, Sushama L., 2016. Lake-river and lake-atmosphere
  interactions in a changing climate over Northeast Canada. EGU, Vienna, Austria.

   \item Duguay C., Sushama L., \textbf{Huziy O.}, Baijnath J., Music B., 2015.
   Representation of large lakes in weather and climate models. CNRCWP Science
   meeting, Montreal.

   \item \textbf{Huziy O.}, Sushama L., 2015. Exploring interflow - soil moisture - climate
   linkages: Case study for northeast Canada. Joint assembly AGU-GAC-MAC-CGU, Montreal.

   \item \textbf{Huziy O.}, Sushama L., Laprise R., 2014. Lake-river-atmosphere Interactions
   as Simulated by the Canadian Regional Climate Model (CRCM5) over North-east
   Canada. AGU Fall meeting, San Francisco.

   \item \textbf{Huziy O.}, Sushama L., Laprise R., 2014. Lakes and rivers in
   CRCM5 and 3D simulations of The Great Lakes. CNRCWP Science meeting, Montreal

   \item \textbf{Huziy O.}, Sushama L., Khaliq M.N., Laprise R., Lehner B. and Roy
    R., 2013. Analysis of streamflow characteristics over northeastern Canada in a
    changing climate. Canadian Meteorological and Oceanographic Society (CMOS),
    Saskatoon.

   \item \textbf{Huziy O.}, Sushama L. and Laprise R., 2013. Impact of lakes
   and rivers on the regional climate and hydrology of northeast Canada.
   Workshop on Regional Climate modelling and Diagnostics, UQAM, Montreal.

    \item \textbf{Huziy O.}, Sushama L., Khaliq M.N., Lehner B., Laprise R., Roy
    R., "Analysis of Streamflow Characteristics over Northeastern Canada in a
    Changing Climate", poster presentation at CMOS conference, Montreal, 28 May -
    1 June 2012.

    \item \textbf{Huziy O.}, Sushama L., Khaliq M.N., Lehner B., Laprise R., Roy
    R.: "Projected Changes to Streamflow Characteristics in North-East Canadian
    Basins as Simulated by the Canadian Regional Climate Model (CRCM4)", poster
    presentation at AGU Fall meeting, San Francisco, December 5, 2011.

    \item \textbf{Huziy O.}, Clavet-Gaumont J., Sushama L., Khaliq M.N., Lehner
    B., Laprise R., Roy R.: "Projected changes to streamflow extremes in Quebec
    basins as simulated by the Canadian Regional Climate Model (CRCM4)",
    presentation at workshop at ESCER, UQÀM, Montreal (QC), May 25, 2011,
    (\url{http://people.sca.uqam.ca/~huziy/pdf/Workshop_UQAM_2011.pdf}).

    \item \textbf{Guziy A.M. (Huziy O. M.)}, Kovalets I.V., Kushchan A.A.,
    Zheleznyak M.J.
    "Statistical downscaling of results of the forecasting system MM5–Ukraine using neural net technology.",
    workshop presentation, Saint-Petersburg, 2008, (\url{http://people.sca.uqam.ca/~huziy/pdf/presentation_spb2008.pdf}).

\end{itemize}
}
