\vspace{\vertspace}


{
\renewcommand{\labelitemi}{}
\begin{itemize}

    \item \textbf{Huziy O}, Teufel B, Sushama L, Yerubandi R, 2021: "Heavy Lake-Effect Snowfall Changes and Mechanisms 
    for the Laurentian Great Lakes Region. Atmosphere", 12(12):1577.

    \item Teufel B., Sushama L., \textbf{Huziy O.} et al., 2019: "Investigation of the mechanisms leading to the 2017 Montreal flood.",
    Clim Dyn 52, 4193-4206. 

    \item Diro, G. T., Sushama L., \textbf{Huziy O.}, 2017: "Snow-atmosphere coupling and its impact
    on temperature variability and extremes over North America.", Climate Dynamics.

    \item Teufel B., Diro G.T., Whan K., Milrad S.M., Jeong D.I., Ganji A.,
    \textbf{Huziy O.}, Winger K., Gyakum J.R., de Elia R., Zwiers F.W., Sushama
    L., 2015: "Investigation of the 2013 Alberta flood from weather and climate
    perspectives", Climate Dynamics.

    \item \textbf{Huziy O.} and Sushama L., 2015: "Lake-river and
    lake-atmosphere interactions in a changing climate over Northeast Canada",
    Climate Dynamics.

    \item \textbf{Huziy O.} and Sushama L., 2015: "Impact of lake-river
    connectivity and interflow on the Canadian RCM simulated regional climate
    and hydrology for Northeast Canada", Climate Dynamics.

    \item Clavet-Gaumont J., Sushama L., Khaliq M.N.,
    \textbf{Huziy O.}, Roy R., 2013: "Canadian RCM projected changes to high
    flows for Québec watersheds using regional frequency analysis", International Journal of Climatology.

    \item \textbf{Huziy O.}, Sushama L., Khaliq M.N., Bernhard
    Lehner, René Laprise, Roy R., 2013: "Analysis of Streamflow Characteristics over Northeastern Canada
     in a Changing Climate", Climate Dynamics, DOI:
     10.1007/s00382-012-1406-0.

\end{itemize}
}
